---
title       : Developing Data Products Project
subtitle    : Data Science Specialization
author      : misket
job         : Coursera
logo        : devApp.jpg
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Let's Begin

1. I have nothing to pitch here
2. So I'll try to do some random ranting and playing aound
3. Here goes nothing!

--- .class #id 

## Let's play around a little with mathematical expressions

- I want to begin with expressing how much I like $\pi$. It is a wonderful number and you encounter it virtually everywhere.

- Its value is beyond my grasp. But is begins elegantly with $3.1416..$ and has no end.

- Did you know: $$\frac{22}{7} \approxeq \pi$$ Cool isn't it!

--- &radio

## Now let's try the interactive elements

What is the answer to **1 Answer to the Ultimate Question of Life, the Universe, and Everything**?

1. 55
2. 93
3. 77
5. _42_
4. All of the above
4. None of the above
5. some of the above

*** .hint 
You know the answer just *Don't Panic*

*** .explanation 
Don't forget your **towel** before moving ahead!

--- &twocol

## Let's embed an R code that does nothing useful!

*** =left

Let's try and load a library
```{r}
library(ggplot2)
data(mtcars)
```
Finally a neat looking plot
```{r, }
plot <- ggplot(mtcars, aes(wt, mpg)) + 
            geom_point(aes(colour = as.factor(gear))) + 
            stat_smooth(method = "lm") +
            labs(x = "Car Weight (1000lbs)", y = "MPG",
                 colour = "Num. of Gears")
```

I could not understand why it echoes to the center?
*** =right

```{r, echo = FALSE}
plot
```
